Computing Entropies With Nested Sampling

### 2017-05-26 paper/ms.tex
Fixing up volume stuff

\renewcommand{\d}{\boldsymbol{d}}
\newcommand{\todo}{\color{orange} \bf}
\newcommand{\query}{\color{green} \bf}
\newcommand{\x}{\boldsymbol{\theta}}
\newcommand{\bphi}{\boldsymbol{\phi}}
\newcommand{\boldeta}{\boldsymbol{\eta}}
\newcommand{\n}{\boldsymbol{\eta}}

@@

For experimental design purposes, if we want to maximise the expected amount
of information obtained from data, maximising either $I_{\x, \d}$ or
$H_{\x | \d}$ will produce the same result because the prior $p(\x)$ does not
vary with the experimental design. Reference priors {\bf cite Bernardo}
also make use of the mutual information but in a different way.

@@

Continuous hypothesis spaces are commonly used in practice. Suppose
$\x$ has probability density $f(\x)$, so the differential entropy is
\begin{align}
H &= -\int_{-\infty}^{\infty} f(\x) \log f(\x) \, d\x
\end{align}

What the algorithm actually estimates is
\begin{align}
h &= \int f(\x) \int f(\x')
            \log \left[ P(d(\x', \x) < L | \x) \right]
                        \, d\x' \, d\x.
\end{align}
If we actually want the differential
entropy, we can use the fact that density equals mass divided
by volume. Assume $L$ is small, so that
\begin{align}
P(d(\x', \x) < L | \x)
    &\approx
    f(\x) \int_{d(\x', \x) < L} \, d\x'\\
    &= f(\x) \, V
\end{align}
where $V$ is the volume of the region where $d(\x', \x) < L$.

In a one-dimensional parameter space, the algorithm will calculate
\begin{align}
h(L) &= \int f(\x) \int f(\x')
             \log \left[ \int_{x - L}^x f(x') \right]
                        \, d\x' \, d\x.
\end{align}
See the Appendix for a discussion of this quantity. To obtain the differential
entropy, compute $h(L)$ for small $L$ and then add $\log(L)$.

@@

From the algorithm, the expected log-probability was
\begin{align}
?_{\d} &= 928.80 \pm 0.38.
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential entropy was

>>>>

\renewcommand{\d}{\boldsymbol{d}}
\newcommand{\todo}{\color{orange} \bf}
\newcommand{\query}{\color{green} \bf}
\newcommand{\x}{\boldsymbol{\theta}}
\newcommand{\bphi}{\boldsymbol{\phi}}
\newcommand{\boldeta}{\boldsymbol{\eta}}
\newcommand{\n}{\boldsymbol{\eta}}
\newcommand{\depth}{\textnormal{depth}}

@@

For experimental design purposes, if we want to maximise the expected amount
of information obtained from data, maximising either $I_{\x, \d}$ or
$H_{\x | \d}$ will produce the same result because the prior $p(\x)$ does not
vary with the experimental design. Reference priors
\citep{bernardo2005reference} also make use of the mutual information but in a
different way.

@@

Continuous hypothesis spaces are commonly used in practice. Suppose
$\x$ has probability density $f(\x)$. The algorithm actually estimates
the `depth', or minus the expected value of the log-probability near $x$:
\begin{align}
h &= -\int f(\x) \int f(\x')
            \log \left[ P(d(\x', \x) < L | \x) \right]
                        \, d\x' \, d\x.
\end{align}
for some tolerance $L$.

If we actually want the differential
entropy
\begin{align}
h_{\x} &= -\int f(x) \log f(x) \, dx
\end{align}
we can use the fact that density equals mass divided
by volume. Assume $L$ is small, so that
\begin{align}
P(d(\x', \x) < \epsilon | \x)
    &\approx
    f(\x) \int_{d(\x', \x) < L} \, d\x'\\
    &= f(\x) \, V
\end{align}
where $V$ is the volume of the region where $d(\x', \x) < L$.

If the distance function $d(\x', \x)$ is chosen to be Euclidean,
the constraint $d(\x', \x) < L$ corresponds to a ball in the space
of possible $\x'$ values.
The log-volume of a ball of radius $L$ in $n$ dimensions is
\begin{align}
\log V(\epsilon; n) &= \frac{n}{2}\log \pi
                        - \log \Gamma\left(\frac{n}{2} + 1\right)
                        + n \log L,
\end{align}
and provides the conversion factor between the differential entropy and
the entropy actually computed from the algorithm.

If $L$ is not small, we might think we are calculating the entropy associated
with the question `what is $x$, to within a tolerance of $\pm L$?'.
This is not quite correct. See the Appendix for a discussion of this
type of question.

@@

From the algorithm, the expected log-probability was
\begin{align}
\depth_{\d} &= 928.80 \pm 0.38.
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential entropy was
